Assessment of the ability to track changes for nowcasts, measurements, and forecasts

### 2024-04-10 paper.tex
Update on Overleaf.

This paper focuses on pure \ac{aatc} accompanying traditional scores.
The \ac{aatc} adds valuable information on the methods' capability of predicting the development of the target value, for example, the number of cases of an epidemic, where increases can be an early sign of the beginning of a wave.

In this article, we formalize \ac{atc} and present different variants of \acs{aatc} measures that consider either noiseless data or data with noise and small non-informative changes (see Section~\ref{sec:aatc}).
We introduce the conditional \ac{atc} plot, a new graphical method for assessing local \ac{atc} behavior, and review bootstrap methods for calculating confidence intervals (see Section~\ref{subsec:aatc-noise} and ~\ref{subsec:aatc-cond-prob}).
We extend the concept of \ac{aatc} to probabilistic predictions in Section~\ref{subsec:aatc-probabilistic}.
The methods are applied to three applications from the abovementioned fields: COVID-19-nowcasting, emergency department arrival forecasting, and blood pressure measurement, and, thus, provide blueprints for future assessments.
The ready-to-use code for \ac{aatc} from the applications is available on [LINK WILL BE INSERTED].

\section{\ac{aatc}}\label{sec:aatc}

>>>>

This paper focuses on pure \ac{aatc} accompanying traditional scores.
The assessment of \ac{atc} adds valuable information on the methods' capability of predicting the development of the target value, for example, the number of cases of an epidemic, where increases can be an early sign of the beginning of a wave.

In this article, we formalize \ac{atc} and present different variants of assessment of \ac{atc} measures that consider either noiseless data or data with noise and small non-informative changes (see Section~\ref{sec:aatc}).
We introduce the conditional \ac{atc} plot, a new graphical method for assessing local \ac{atc} behavior, and review bootstrap methods for calculating confidence intervals (see Section~\ref{subsec:aatc-noise} and ~\ref{subsec:aatc-cond-prob}).
We extend the concept of assessment of \ac{atc} to probabilistic predictions in Section~\ref{subsec:aatc-probabilistic}.
The methods are applied to three applications from the abovementioned fields: COVID-19-nowcasting, emergency department arrival forecasting, and blood pressure measurement, and, thus, provide blueprints for future assessments.
The ready-to-use code for the assessment of \ac{atc} from the applications is available on [LINK WILL BE INSERTED].

\section{Assessment of the \acf{atc}}\label{sec:aatc}
